## Quantile regression average

NB: This is a transient package that will probably be merged into the
[stackr package](https://github.com/nikosbosse/stackr). 

## Prerequisites

This depends on the [scoringutils](https://github.com/epiforecasts/scoringutils)
package, which can be installed with 

```{r eval=FALSE}
remotes::install_github("epiforecasts/scoringutils")
```

The code itself can be tested by installing the corresponding package:
```{r eval=FALSE}
remotes::install_github("epiforecasts/qra")
```


### Create the forecast/data structure

We will create 3 weeks of daily (toy) forecasts, produced at 3 different dates in May.
There will be (toy) forecasts at a regional and national level.
national level

```{r}
library("qra")
library("dplyr")
library("tidyr")
library("readr")
df <- tidyr::expand_grid(
                      value_type = c("cases", "deaths"),
                      geography = c(paste("region", 1:3), "country"),
                      creation_date = as.Date(c("2020-05-11",
                                                "2020-05-18",
                                                "2020-05-25")),
                      horizon = 1:21) %>%
  dplyr::mutate(value_date = creation_date + horizon) %>%
  dplyr::select(-horizon) %>%
  dplyr::mutate(geography_scale =
           dplyr::if_else(grepl("region", geography), "region", "nation"))
```

### create toy "forecasts" (draws from negative binomial distributions)

```{r}
mean <- c(10L, 20L, 30L, 40L, 50L)
k <- c(0.5, 1, 1.5, 2, 3)
quantile_levels <- seq(0.05, 0.95, by = 0.05)

flist <- lapply(seq_along(mean), function(x) {
  df %>%
    rowwise() %>%
    dplyr::mutate(model = paste("model", x),
                  quantiles = list(as_tibble(t(setNames(
                    qnbinom(quantile_levels, size = 1/k[x], mu = mean[x]),
                    paste0("quantile_", quantile_levels)))))) %>%
    tidyr::unnest(quantiles) %>%
    tidyr::pivot_longer(names_to = "quantile", starts_with("quantile_")) %>%
    dplyr::mutate(quantile = readr::parse_number(quantile))
})

forecasts <- flist %>%
  dplyr::bind_rows()
```

### create toy "data"

```{r}
true_mean <- 25L
true_k <- 2
data <- df %>%
  select(value_type, geography, value_date) %>%
  distinct() %>%
  mutate(value = rnbinom(n(), true_mean, 1/true_k))
```

### calculate QRA

Forecasts are pooled by forecast horizon and geography, use last <14 days of
forecasts for optimising the weights.
```{r}
res <- qra::qra(forecasts %>%
                filter(model == "model 1"),
                data, pool = c("horizon", "geography"),
                min_date = max(forecasts$creation_date) - 13)
```
